%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Software Engineering Intern} % Job title
  {Meta} % Organization
  {London, UK} % Location
  {Jul 2022 -- Oct 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item Used Hack, React.js and GraphQL to implement new internal tool for searching for customer support cases, performing
      quick actions on them and displaying relevant data and pages, freeing tens of man-hours per day across the org.
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Software Engineering Intern} % Job title
  {Yandex} % Organization
  {Moscow, Russia} % Location
  {Jul 2021 -- Oct 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item Developed Python gRPC client library to send requests to microservice management system to replace a separate executable,
      reducing request time by 85\% and number of lines of code required to make requests by 50\%.
      \item Reworked logging system, resulting in 1000 lines codebase size reduction, improving readability, decreasing complexity
      and providing new possibilities for enforcing thread safety, helping fix race condition in multiple unit tests.
      \item Introduced static code style checks for project with 50'000 lines of C++ code and refactored project to comply with new requirements.
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Software Engineering Intern} % Job title
  {Sibur} % Organization
  {Moscow, Russia} % Location
  {Sep 2020 -- Dec 2020} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item Proposed location and workday data gathering pipeline, getting data from more than 1500 employees. Prepared it for route finding algorithm using pandas. Created converter from algorithm output to pdf timetables using Python.
      \item Proposed way of transferring large files (up to 10GB) using gRPC, enabling robust data upload to route finding computation unit.
      \item Developed aggregator \href{https://www.sibur.ru/bus/}{website} of bus monitoring links for different cities using React.js, allowing users to easily access relevant link when doing business trips.
      \item Implemented Java library for easier calls to API that enabled automated updates of bus routes, eliminating whole workday of manual work every week.
      \item Created Java library for automation of calculations that were previously carried out in excel, removing human link from production chain, increasing performance and reliability.
    \end{cvitems}
  }

  %---------------------------------------------------------
\end{cventries}
